Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-17 Grassmannian_cells.tex
typo
Minor edits

To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
\begin{lemma}
  \label{le:special subrepresentations}
  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  \begin{enumerate}
    \item For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
      Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
      \[\tilde P_m(I,j):=
        \begin{cases}
          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
        \end{cases}\]
    \item For $m\ge3$, any nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is surjective.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
  Indeed, this gives
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]
  We establish the final claim of part (1) directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
  Using the description in Example~\ref{ex:truncated lifts}, it is not hard to see that $\tau\tilde P_3^I$ is indecomposable with one-dimensional spaces at only the vertices $(1,e)$ and $(2,\alpha_i^{-1})$ for $i\in I$.
  But then for~$j\in I$, the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\]
  From the support quiver of $\tilde P_{2,j}$ given in Example~\ref{ex:lifted preprojectives}, we see that the kernel of this map is precisely $\tilde P_2(I,j)$.

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
\begin{corollary}
  \label{cor:perpendicular}
  Consider a nonempty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
  \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
  From Lemma~\ref{le:properties}.(3) again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.(4), we get
  \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
  It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.(4) again imply 
  \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.

@@

\noindent 
In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
Alternatively, a cell decomposition of $X$ is a collection of disjoint subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union of a subset of the affine cells for $X$.
In this case, $U$ also has a cell decomposition given by taking exactly those affine cells which are contained in $U$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  \label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\end{proof}
The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
If we denote these iterated torus fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
\begin{corollary}
  Let $X$ be a representation which can be lifted to $\tilde Q$.
  Then there exists an iterated torus action such that
  \[\Gr^Q_\bfe(X)^{(k+1)}\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)^{\CC^*}\cong \bigsqcup_{\hat\bfe^{(k+1)}} \Gr^{\hat Q^{(k+1)}}_{\hat\bfe^{(k+1)}}\big(\hat X^{(k+1)}\big)\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X),\]
  where $\hat\bfe^{(k)},\,\hat\bfe^{(k+1)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}

@@

Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any nonempty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.

@@

We will apply these results in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above for any fixed $\tbfe$:
\begin{equation}
  \label{eq:truncated CC}
  \Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
\begin{equation}
  \label{eq:truncated CC2}
  \Phi:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is surjective.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is nonempty in this case.
\end{proof}

>>>>

To emphasize this point, consider a word $\ui\in A_1^{(k)}$ with $i_j=i_{j+1}$ for some $j$ and write $\ui'\in A_1^{(k-2)}$ for the word obtained from $\ui$ by removing the terms $i_j$ and $i_{j+1}$.
Then the representations $\tilde P_{m+1-k,\ui}$ and $\tilde P_{m+1-k,\ui'}$ are in fact equal, however $\tilde P_{m+1-k,\ui}$ is naturally identified as a subrepresentation of $\tilde P_{m+1}$ while $\tilde P_{m+1-k,\ui'}$ is not.
Indeed, by considering the support quiver of $\tilde P_{3,i}$ from Example~\ref{ex:lifted preprojectives}, we see that each $\tilde P_{2,(i,i)}$ is just a copy of $\tilde P_2$ when viewed as representations of $\widetilde{K(n)}$, however these provide distinct subrepresentations of $\tilde P_4$.
\begin{lemma}
  \label{le:special subrepresentations}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$. 
  \begin{enumerate}
    \item For $m\ge2$, we have $\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)\cong\CC$.
      Moreover, the kernel of a nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is the following representation 
      \[\tilde P_m(I,j):=
        \begin{cases}
          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{m-1,(j,i)}\oplus \bigoplus_{i\in I, i\ne j}\tilde P_{m-2,(j,j,i)} & \text{ if $m\geq 3$;}\\
          \bigoplus_{\substack{1\leq i\leq n\\i\neq j}}\tilde P_{1,(j,i)} & \text{ if $m=2$.}
        \end{cases}\]
    \item For $m\ge3$, any nonzero morphism $\tilde P_{m,j}\to\tau\tilde P_{m+1}^I$ is surjective.
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first claim of part (1) follows immediately by applying the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} to Lemma~\ref{le:properties}.(3).
  Indeed, this gives
  \[\dim\Hom(\tilde P_{m,j},\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})=1.\]
  We establish the final claim of part (1) directly for $m=2,3$ and then deduce the general case by applying the reflection recursions \eqref{eq:recursive covers}.
  Using the description in Example~\ref{ex:truncated lifts}, it is not hard to see that $\tau\tilde P_3^I$ is indecomposable with one-dimensional spaces at only the vertices $(1,e)$ and $(2,\alpha_i^{-1})$ for $i\in I$.
  But then for~$j\in I$, the image of the unique homomorphism $\tilde P_{2,j}\to\tau\tilde P_3^I$ is the representation with support quiver
  \[(2,\alpha_j^{-1})\xrightarrow{\alpha_j}(1,e).\]
  From the support quiver of $\tilde P_{2,j}$ given in Example~\ref{ex:lifted preprojectives}, we see that the kernel of this map is precisely $\tilde P_2(I,j)$.

@@

The following orthogonality property is a primary reason we need to lift to the universal cover of $K(n)$.
\begin{corollary}
  \label{cor:perpendicular}
  Consider a non-empty subset $I\subsetneq\{1,\ldots,n\}$ and fix an element $j\in I$.
  For $m\geq 2$, we have $\tilde P_m(I,j)\in (\tilde P_{m+1}^I)^\perp$.
\end{corollary}
\begin{proof}
  If $m\geq 3$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m+1}^I,-)$ to the sequence
  \[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tau\tilde P_{m+1}^I}.\]
  Following Lemma~\ref{le:properties}.(3), we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$ and using the long exact sequence this immediately implies $\Hom\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.
  From Lemma~\ref{le:properties}.(3) again, we have $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC$.
  Using the Auslander-Reiten formulas \cite[Theorem IV.2.13]{ass} and Lemma~\ref{le:properties}.(4), we get
  \[\dim\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Hom(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=1.\]
  It follows that the surjective map $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\to\Ext(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)$ appearing in the long exact sequence is in fact an isomorphism.
  But the Auslander-Reiten formulas and Lemma~\ref{le:properties}.(4) again imply 
  \[\dim\Hom(\tilde P_{m+1}^I,\tau\tilde P_{m+1}^I)=\dim\Ext(\tilde P_{m+1}^I,\tilde P_{m+1}^I)=0.\]
  Combining with the preceding discussion, this gives $\Ext\!\big(\tilde P_{m+1}^I,\tilde P_m(I,j)\big)=0$.

@@

\noindent 
In this section, we aim to establish the existence of cell decompositions for quiver Grassmannians of (truncated) preprojective representations of $K(n)$ and its universal covering quiver.
By a \emph{cell decomposition} of an algebraic variety $X$, we mean a filtration $\varnothing=X_{k+1}\subset X_k\subset \cdots \subset X_2\subset X_1=X$ of $X$ by closed subsets $X_i\subset X$ so that each $X_i\setminus X_{i+1}$ is isomorphic to an affine space.
Alternatively, a cell decomposition of $X$ is a collection of disjoint locally closed subsets $U_1,\ldots,U_k\subset X$, each isomorphic to an affine space, such that each $X_i=U_i\sqcup U_{i+1}\sqcup\cdots\sqcup U_k$ is closed in $X$ with $X_1=X$.
We call the subsets $U_i\subset X$ the \emph{affine cells} for this cell decomposition.
Given varieties $X$ and $Y$ each with cell decompositions, we may choose an ordering on products of their affine cells (e.g.\ lexicographic) to get a cell decomposition of $X\times Y$. 
Given a variety $X$ with a cell decomposition, we call a subvariety $U\subset X$ \emph{compatible} with the cell decomposition if $U$ can be written as the union over a subset of the affine cells for $X$.
In this case, $U$ also has a cell decomposition given by taking exactly those affine cells for $X$ which are contained in $U$.

@@

In the following, we say that $d:\supp(\hat X)\to\ZZ$ satisfies the \emph{degree condition} for $\hat X$ if it has the properties of Lemma~\ref{le:degree condition}.
\begin{theorem}
  \label{thm:torusfixedpoints}
  Let $X$ be a representation of $Q$ which can be lifted to a representation $\hat X$ of $\hat Q$ and choose $d:\supp(\hat X)\to\ZZ$ such that it satisfies the degree condition for $\hat X$.
  Then the $\CC^*$-action on $\bigoplus_{i\in Q_0} X_i$ determined by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a $\CC^*$-action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^{\CC^*}\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a $\CC^*$-fixed point if and only if $t.U=U$ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$ and all $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, each component $U_i$ is a fixed point of the induced $\CC^*$-actions on the usual Grassmannians of vector subspaces $\Gr_{\bfe_i}(X_i)$.
  By Lemma~\ref{le:usualGrass}, this holds precisely when we have a decomposition 
  \[U_i=\bigoplus_{\chi\in A_Q} U_i\cap X_{(i,\chi)}\]
  which is equivalent to $U$ being liftable to the universal abelian covering $\hat Q$.
\end{proof}
The next step is to iterate the $\CC^*$-actions, keeping in mind the following idea: every representation $X$ which lifts to the universal covering quiver also lifts to the universal abelian covering quiver and to the iterated universal abelian covering quivers, i.e.\ to each $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q^{(1)}:=\hat Q$.
Now it is straightforward to check that there exist natural surjective morphisms $f_k:\widetilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}.
Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 0$ such that the full subquiver with vertices $\supp(X)\subseteq \hat Q^{(k+1)}_0$ is a tree.
Thus, writing $\hat X^{(\ell)}$ for the lift of $X$ to $\hat Q^{(\ell)}$, there exists a $\CC^*$-action on the vector spaces $\hat X^{(k)}_\beta$ for $\beta\in \hat Q^{(k-1)}_0\times A_{\hat Q^{(k-1)}}$ which induces $\CC^*$-actions on the quiver Grassmannians $\Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)$ such that the fixed point sets are precisely $\Gr_{\hat\bfe^{(k+1)}}^{\hat Q^{(k+1)}}\big(\hat X^{(k+1)}\big)$.
If we denote these iterated $\CC^*$-fixed points by $\Gr^Q_\bfe(X)^{(k+1)}$, we obtain the following result.
\begin{corollary}
  Let $X$ be a representation which can be lifted to $\tilde Q$.
  Then there exists an iterated torus action such that
  \[\Gr^Q_\bfe(X)^{(k+1)}\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr_{\hat\bfe^{(k)}}^{\hat Q^{(k)}}\big(\hat X^{(k)}\big)^{\CC^*}\cong \bigsqcup_{\hat\bfe^{(k+1)}} \Gr^{\hat Q^{(k+1)}}_{\hat\bfe^{(k+1)}}\big(\hat X^{(k+1)}\big)\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X),\]
  where $\hat\bfe^{(k)},\,\hat\bfe^{(k+1)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}

@@

Let $\ses{M}{B}{N}$ be a short exact sequence of representations.
For a fixed dimension vector $\tbfe$, this induces the so-called ``Caldero-Chapoton map'' between quiver Grassmannians
\begin{align*}
  \Psi:\Gr_\tbfe(B)&\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr_\tbff(M)\times \Gr_\tbfg(N)\\
  E&\mapsto \big(E\cap M,(E+M)/M\big).
\end{align*}
Following \cite[Section 3]{cc}, any non-empty fiber of $\Psi$ satisfies $\Psi^{-1}(U,W)\cong\mathbb{A}^{\dim\Hom(W,M/U)}$.

@@

We will apply these results in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For fixed subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above for any fixed $\tbfe$:
\begin{equation}
  \label{eq:truncated CC}
  \Psi:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then, in the same way as above, we obtain the following map for any fixed $\tbff$:
\begin{equation}
  \label{eq:truncated CC2}
  \Phi:\Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\to\bigsqcup_{\tbfs+\tbft=\tbff} \Gr^{\tilde Q}_\tbfs\big(\tilde P_m(I,j)\big)\times\Gr^{\tilde Q}_\tbft(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a non-empty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ being non-empty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

  If $W\neq 0$, $\tilde K_m/W$ is a proper factor of $\tilde K_m$ and we must have $\Ext(\tilde P_{m+1}^I,\tilde K_m/W)=0$.
  Indeed, by Auslander-Reiten theory every non-split morphism $g:\tilde K_m\to\tilde K_m/W$ factors through the middle term $Z$ of the AR-sequence 
  \begin{equation}
    \label{eq:ar2}
    \ses{\tilde K_m}{Z}{\tilde P_{m+1}^I}.
  \end{equation}
  This in particular says the first map of the induced sequence
  \[\Hom(Z,\tilde K_m/W)\to\Hom(\tilde K_m,\tilde K_m/W)\to\Ext(\tilde P_{m+1}^I,\tilde K_m/W)\to\Ext(Z,\tilde K_m/W)\]
  is surjective.
  By Lemma~\ref{le:properties}.(4) and the Auslander-Reiten formulas, we have 
  \[\Ext(\tilde K_m,\tilde K_m)=0\qquad\text{and}\qquad\Ext(\tilde P_{m+1}^I,\tilde K_m)=\CC.\]
  For $m=2$, the identities above follow immediately from the corresponding statements for $\tau\tilde P_3^I$.
  Thus the injective map $\CC=\Hom(\tilde K_m,\tilde K_m)\to\Ext(\tilde P_{m+1}^I,\tilde K_m)$ induced by the Auslander-Reiten sequence \eqref{eq:ar2} is actually bijective and so applying $\Hom(-,\tilde K_m)$ to this sequence yields $\Ext(Z,\tilde K_m)=0$.
  But then $\Ext(Z,\tilde K_m/W)=0$ and so $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\cong\Ext(\tilde P_{m+1}^I,\tilde K_m/W)$ must be zero as well.
  By part (1) we see that the fiber $\Psi^{-1}(U,\tilde P_{m+1}^I)$ is non-empty in this case.
\end{proof}
